### 2021-09-15 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@d132640e15855776d2d8d7e9febd6db8ab493aa0 🚀

There are two core challenges we are faced with in furthering our
understanding of ecological networks across space, particularly at
macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen
2016). First, networks within a location are difficult to sample
properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
shortfall'' (Hortal \emph{et al.} 2015), \emph{i.e.} a lack of knowledge
about inter and intra specific relationships. This first challenge has
been, in large part, addressed by the recent emergence of a suite of
methods aiming to predict interactions within \emph{existing} networks,
many of which are reviewed in Strydom \emph{et al.} (2021a). Second,
recent analyses based on collected data (Poisot \emph{et al.} 2021a) or
metadata (Cameron \emph{et al.} 2019) highlight that ecological networks
are currently studied in a biased subset of space and bioclimates, which
impedes our ability to generalize any local understanding of network
structure. Meaning that, although the framework to address
incompleteness \emph{within} networks exists, there would still be
regions for which, due to a \emph{lack} of local interaction data, we
are unable to infer potential species interactions. Having a general
solution for inferring a \emph{plausible} metaweb (despite the
unavailability of interaction data) could be the catalyst for
significant breakthroughs in our ability to start thinking about species
interactions networks over large spatial scales.

>>>>

There are two core challenges we are faced with in furthering our
understanding of ecological networks across space, particularly at
macro-ecologically relevant scales (\emph{e.g.} Trøjelsgaard \& Olesen
2016). First, networks within a location are difficult to sample
properly (Jordano 2016a, b), resulting in a widespread ``Eltonian
shortfall'' (Hortal \emph{et al.} 2015), \emph{i.e.} a lack of knowledge
about inter and intra specific relationships. This first challenge has
been, in large part, addressed by the recent emergence of a suite of
methods aiming to predict interactions within \emph{existing} networks,
many of which are reviewed in Strydom \emph{et al.} (2021a). Second,
recent analyses based on collected data (Poisot \emph{et al.} 2021a) or
metadata (Cameron \emph{et al.} 2019) highlight that ecological networks
are currently studied in a biased subset of space and bioclimates, which
impedes our ability to generalize any local understanding of network
structure. Meaning that, although the framework to address
incompleteness \emph{within} networks exists, there would still be
regions for which, due to a \emph{lack} of local interaction data, we
are unable to infer potential species interactions. Having a general
solution for inferring a \emph{plausible} metaweb (despite the
unavailability of interaction data) could be the catalyst for
significant breakthroughs in our ability to start thinking about species
interaction networks over large spatial scales.
